Software Citation Principles

### 2016-07-23 sc-principles/software-citation-principles.tex
added description for use case 15

>>>>

In this use case, an evaluator (e.g., academic administrator) or funder wants
to evaluate the contributions of a researcher who develops software. This case
is related to those where researchers want to get credit for software
development, or where organizations want to evaluate the impact of software
itself.
